InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-28 paper.tex
add text

\subsubsection{Image generating models}
The first image generating model we us is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

@@

>>>>

\subsubsection{Image generating models}

@@

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset. swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{https://arxiv.org/pdf/2103.14030.pdf}.
